Threat detection in online discussions

### 2016-05-03 submission.tex
updated author list

% Author information can be set in various styles:
% For several authors from the same institution:
\author{Aksel Wester \and Lilja Øvrelid \and Erik Velldal \\
  Department of Informatics \\
  University of Oslo, Norway \\
  \{aksellw, liljao, erikve\}@ifi.uio.no}
% if the names do not fit well on one line use

>>>>

%\clubsuit

% Author information can be set in various styles:
% For several authors from the same institution:
%\author{Aksel Wester \and Lilja Øvrelid \and Erik Velldal \\
%  Department of Informatics \\
%  University of Oslo, Norway \\
%  \{aksellw, liljao, erikve\}@ifi.uio.no}
% if the names do not fit well on one line use

% Author information can be set in various styles:
% For several authors from the same institution:
\author{Aksel Wester$^1$ \and Lilja Øvrelid$^1$ \and Erik Velldal$^1$ \and Hugo Lewi Hammer$^2$\\[1ex]
  ${}^1$ Department of Informatics\\ University of Oslo\\
  {\smaller {\tt \{aksellw, liljao, erikve\}@ifi.uio.no}}\\[1ex]
${}^2$ Department of Computer Science\\ Oslo and Akershus University College of Applied Sciences\\
{\smaller{\tt hugo.hammer@hioa.no}}}
% if the names do not fit well on one line use
